A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-07-26 draft/paper2_v3.tex
Edit result 3

    The left panel of Fig~\ref{fig:scaling_relation} shows the \mtot{}--$R_{\mathrm{50}}$
    relations for galaxies in high and low mass dark matter halos. We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
    likelihood estimates, and we assume flat priors for parameters.}.

@@

    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, galaxies in low and high mass haloes live on \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but different normalizations. This result is robust against the ranges of \mstar{} over which the fit is performed and against the definitions 
    of  ``total'' \mstar{} and half-light radius\footnote{Using \mstar{} within 120 or 
    150 kpc, or using the $R_{\mathrm{50}}$ derived within these apertures does not 
    change the results.}.

    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
    green solid line) who studied $z\leq 0.09$ central ETGs in 
    $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13 use the group catalog by \citet{Yang2007} to estimate halo mass. They obtain effective radii from  single-\ser{} model fitting to SDSS 
    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic offset between BC03 and our FSPS model (see Paper~1). 
    The distributions of galaxies on the 
    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
    (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
    start to become incomplete. 
    In contrast to the present study, HC13 finds no environment dependence in the 
    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$. However, HC13 use SDSS which is considerably shallower compared the HSC and hence will not be as sensitive to the outer portions of the profile where we see the largest differences. A more detailed comparison is beyond the scope of this work, but we briefly \alexie{we demsontrate what exactly? chat about this test}
    demonstrate this using the \rbcg{} and \nbcg{} galaxies that overlap with the GAMA
    survey (please see Appendix~\ref{app:gama} for details).

    We matched the two samples using the \mstar{} measured using single-\ser{} 2-D
    model by the GAMA team (\citealt{Kelvin2012}). 
    At fixed \mgama{}, the \rbcg{} galaxies display much more significant stellar 
    halo despite they have very similar inner \mden{} profiles.  
    This shows again that the deeper HSC images has unique advantage in studying the
    connection between the assembly of massive galaxies and their dark matter haloes.

@@

    Now we investigate the relationship \mtot{}, \minn{}, and halo mass. Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued by the ambiguity of galaxy ``size'', and also enables a more straightforward comparison with numerical simulations.

    The right panel of Fig \ref{fig:scaling_relation} compares \rbcg{} and \nbcg{}
    galaxies on the \mtot{}--\minn{} plane. We find that these two samples are offset when considered in this plane a follow distinct best-fit \mtot{}--\minn{} relations. 
    For \rbcg{} galaxies with \logmtot{}$>11.6$ we find:

@@

    These results are robust against the exact choice for the \mtot{} range over which the fit is performed. These results are also unchanged if \minn{} is replaced by mass within a 5 or a 15 kpc aperture, or if \mtot{} is replaced with mass within a 120 or a 150 kpc aperture.

@@

    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in the previous section, namely that: at fixed \mtot{}, central galaxies in more massive haloes tend to have less galaxy mass in the inner regions but display more prominent outer envelopes. The scientific implication of this result is discussed in 
    Section~\ref{sec:discussion}.

\alexie{This seems too detailed. This also belongs in the discusison section}

    Meanwhile, we find \rbcg{} galaxy tends to have lower \mstar{} within 10--15 kpc 
    and shallower inner \mden{} profile than the \nbcg{} one at fixed \mtot{}. 
    Although the HSC can not resolve the central region of these massive galaxies, 
    such difference could have interesting physical implications. 
    Observations of compact quiescent galaxies at high-$z$ tend to suggest higher 
    \mden{} in the central region than their descendants, hence it is necessary to 
    have certain process to reduce the central \mden{} (e.g. strong adiabatic expansion 
    induced by powerful AGN feedback; \citealt{Fan2008}) to match the inner \mden{} 
    profiles of massive central galaxies at low-$z$.
    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
    common in the assembly history of massive galaxies, can also flatten the central 
    \mden{} profile via efficient scattering effect (e.g. \citealt{Milosavljevi2002}).
    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 
    with very low \minn{} at high \mtot{} end that are apparently not bothered by 
    problematic photometry or exceptionally bad seeing.  
    They may be similar to the recently discovered massive BCGs with very large core 
    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) resulting from SMBH mergers.
    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
    topic to investigate in the future.
%% ------------------------------------------------------------------------------------ %%

@@

    In Paper~1, we show that the ellipticity of the outer stellar halo increases with \mtot{}, while in contrast, rest--frame color gradients do not display any strong \mtot{}-dependencies. In this paper, we take this analysis one step further to investigate whether or not either of these quantities display a halo mass dependency. We focus on ellipticity and color profiles within 5--60 kpc where we can ignore differences in sky subtraction and seeing across different bands. Galactic extinction and $k$-corrections are applied to both $(g-r)$ and $(g-i)$ color profiles.

    Figure \ref{fig:ell_color} shows the average ellipticity, $g-r$, and $g-i$ color profiles for galaxies living in low and high mass haloes both at fixed \mtot{} and at fixed \minn{}. We also compared our results with previous studies that stacked SDSS images (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}). Figure \ref{fig:ell_color} shows that:

    \begin{itemize}
        \item \alexie{discuss here}. Galaxies in low and high mass haloes display similar ellipticity profiles at fixed \mtot{}. There is hint that suggests the central galaxies from more massive 
            haloes become slightly more elongated at $R>50$ kpc than the ones 
            in less massive haloes with similar \mtot{}. 
            However, the uncertainties in the current profiles make it not 
            conclusive.              
        \item For the \minn{}-matched samples, the \rbcg{} galaxies show higher
            average ellipticity than the \nbcg{} ones at $R > 10$ kpc. 
            The average ellipticities in the inner region are very similar. 
            This further suggests that the more elongated outer stellar haloes 
            of massive haloes relate to the accreted stars.         
        \item Galaxies in low and high mass dark matter haloes display similar rest--frame color gradients (at $r<60$ kpc) at fixed \mtot{} and at fixed  \minn{}.    
    \end{itemize}

    Besides these conclusions, the fact that we find  smooth ellipticity profile and its shallow gradient supports 
            the idea of using the flux-weighted average isophotal shape to 
            extract 1-D profiles of massive galaxies.

     The similarity of average rest-frame color profiles between the 
            \rbcg{} and \nbcg{} samples suggests that \mden{} profiles based on 
            single average \m2l{} will not bias our comparisons.

>>>>

    The left panel of Fig~\ref{fig:scaling_relation} shows the 
    \mtot{}--$R_{\mathrm{50}}$ relations for galaxies in more and less massive
    dark matter halos. 
    We fit the \logmtot{}-$\log (R_{\mathrm{50}}/\mathrm{kpc})$ relations at 
    $\log(M_{\star,100})>11.6$ using the \texttt{emcee} MCMC sampler 
    (\citealt{Emcee})\footnote{The initial guesses are based on maximum 
    likelihood estimates, and we assume flat priors for parameters.}.

@@

    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, galaxies 
    in more and less massive dark matter haloes lie on \mtot{}--$R_{\mathrm{50}}$ 
    relations that have similar slopes but different normalizations. 
    This result is robust against the ranges of \mstar{} over which the fit is performed 
    and against the definitions of  ``total'' \mstar{} and half-light 
    radius\footnote{Using \mstar{} within 120 or 150 kpc, or using the 
    $R_{\mathrm{50}}$ derived within these apertures do not change the results.}.

    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
    green solid line) who studied $z\leq 0.09$ central ETGs in 
    $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13 use the group catalog by \citet{Yang2007} to estimate halo mass. 
    They obtain effective radii from single-\ser{} model fitting to SDSS 
    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). 
    We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
    offset between BC03 and our FSPS model (see Paper~1). 
    The distributions of galaxies on the 
    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
    (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
    start to become incomplete in stellar mass. 
    In contrast to the present study, HC13 finds no environment dependence in the 
    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$.     
    However, HC13 use SDSS images that are considerably shallower compared to the HSC 
    ones and hence will not be as sensitive to the outer portions of the \mden{} 
    profile where we see the most clear differences. 
    A more detailed comparison is beyond the scope of this work, but in 
    Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
    with the GAMA survey to briefly demonstrate this point. 
    We show that, for galaxies with similar \mstar{} derived from single-\ser{} 
    models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
    massive dark matter halos actually show more prominent outer stellar halos, 
    hence both of their stellar mass and effective radius are underestimated.  
    This shows again that the deeper HSC images has unique advantage in studying the
    connection between the assembly of massive galaxies and their dark matter haloes.

@@

    Now we investigate the relationship among \mtot{}, \minn{}, and \mhalo{}. 
    Compared to the mass--size relation, the \mtot{}--\minn{} relation is not plagued 
    by the ambiguity of galaxy ``size'', and also enables a more straightforward 
    comparison with numerical simulations.

    The right panel of Fig \ref{fig:scaling_relation} compares \rbcg{} and \nbcg{}
    galaxies on the \mtot{}--\minn{} plane. 
    We find that there is an offset between the overall distributions of these two
    samples and they follow distinct best-fit \mtot{}--\minn{} relations. 
    For \rbcg{} galaxies with \logmtot{}$>11.6$ we find:

@@

    These results are robust against the exact choice for the \mtot{} range over which 
    the fit is performed. 
    These results also will not be altered when we replace the \minn{} with the stellar 
    mass within a 5 or a 15 kpc aperture, or if \mtot{} is replaced with stellar mass 
    within a 120 or a 150 kpc aperture.

@@

    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in 
    the previous section, namely that: 
    at fixed \mtot{}, central galaxies in more massive haloes tend to have smaller 
    fraction of stellar mass in their inner regions and higher \mstar{} in their outer
    stellar haloes. 
    Although the HSC images can not resolve the central region of these massive 
    galaxies, the on average lower \mstar{} within 10 kpc and shallower inner \mden{} 
    profile for massive central galaxies living in more massive haloes are robust 
    results and could have interesting physical implications.
    Meanwhile, at fixed \minn{}--a proxy for the \mstar{} of the ``in situ'' component,
    central galaxies in more massive haloes tend to be more massive and display more 
    prominent stellar haloes. 
    The scientific implication of these results will be discussed in 
    Section~\ref{sec:discussion}.

    \todo{Move to discussion}
    Observations of compact quiescent galaxies at high-$z$ tend to suggest higher 
    \mden{} in the central region than their descendants, hence it is necessary to 
    have certain process to reduce the central \mden{} (e.g. strong adiabatic expansion 
    induced by powerful AGN feedback; \citealt{Fan2008}) to match the inner \mden{} 
    profiles of massive central galaxies at low-$z$.
    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
    common in the assembly history of massive galaxies, can also flatten the central 
    \mden{} profile via efficient scattering effect (e.g. \citealt{Milosavljevi2002}).
    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 
    with very low \minn{} at high \mtot{} end that are apparently not bothered by 
    problematic photometry or exceptionally bad seeing.  
    They may be similar to the recently discovered massive BCGs with very large core 
    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) resulting from SMBH mergers.
    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
    topic to investigate in the future.
%% ------------------------------------------------------------------------------------ %%

@@

    In Paper~I, we show that the ellipticity of the outer stellar halo increases with
    \mtot{}, while in contrast, rest--frame color gradients do not display strong 
    \mtot{}-dependencies. 
    In this paper, we take this analysis one step further to investigate whether or 
    not either of these quantities display a halo mass dependency. 
    We focus on ellipticity and color profiles within 5--60 kpc where we can ignore
    differences in sky subtraction and seeing across different filters. 
    Galactic extinction and $k$-corrections are applied to both $(g-r)$ and $(g-i)$ 
    color profiles.

    Figure \ref{fig:ell_color} shows the average ellipticity, $g-r$, and $g-i$ color 
    profiles for galaxies living in more and less massive dark matter haloes both at 
    fixed \mtot{} and at fixed \minn{}. 
    We also compared our results with previous studies that are based on stacked SDSS 
    images (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}). 
    Figure \ref{fig:ell_color} shows that:

    \begin{itemize}
        \item \alexie{discuss here}. Massive central galaxies living in more and 
            less massive haloes display similar ellipticity profiles at fixed \mtot{}. 
            There is hint that suggests the central galaxies from more massive 
            haloes become slightly more elongated at $R>50$ kpc than the ones 
            in less massive haloes with similar \mtot{}. 
            However, the uncertainties in the current ellipticity profiles make it 
            not conclusive.

        \item For the \minn{}-matched samples, the \rbcg{} galaxies show higher
            average ellipticity than the \nbcg{} ones at $R > 10$ kpc. 
            On the other hand, the average ellipticity in the inner region are very 
            similar. 
            This further suggests that the more elongated outer stellar haloes 
            of massive haloes may relate to the accreted stars.

        \item Massive central galaxies in more and less massive dark matter haloes 
            display similar rest--frame color gradients (at $r<60$ kpc) at fixed 
            \mtot{} and at fixed  \minn{}.

    Besides these conclusions, the fact that we find smooth ellipticity profile and 
    its shallow gradient favors the idea of using the flux-weighted average isophotal 
    shape to extract 1-D \mden{} profiles of massive galaxies. 
    The similarity of average rest-frame color profiles between the \rbcg{} and \nbcg{}
    samples suggests that \mden{} profiles based on single average \m2l{} will not bias 
    our comparisons.
